% Proof Map (Bounded-Real Route via Product Certificate)
% Ready to \input into the manuscript; no preamble/macros required.

\section*{Proof Map (Bounded-Real Route via Product Certificate)}

\paragraph{Ambient domain.} Let $\Omega:=\{s\in\mathbb C:\Re s>\tfrac12\}$. Write $s=\tfrac12+\sigma+it$, $\sigma>0$. Let $\xi(s)=\tfrac12 s(1-s)\,\pi^{-s/2}\,\Gamma(\tfrac{s}{2})\,\zeta(s)$.

\paragraph{Objects.} On $\ell^2(\mathcal P)$ let $A(s)e_p:=p^{-s}e_p$. Define the outer-normalized ratio
\[
  \mathcal J(s)\ :=\ \frac{\det\nolimits_2(I-A(s))}{\mathcal O(s)\,\xi(s)},
  \qquad
  \Theta(s)\ :=\ \frac{2\mathcal J(s)-1}{2\mathcal J(s)+1}.
\]
Target: $2\mathcal J$ is Herglotz on $\Omega$ (i.e. $\Re(2\mathcal J)\ge 0$), equivalently $\Theta$ is Schur on $\Omega$.

\paragraph{Window and geometry.} Fix an even $\psi\in C^\infty$ with $\psi\equiv1$ on $[-1,1]$, $0\le\psi\le1$, compact support. For an interval $I=[T-L,T+L]$ with $L\le 1/\log\langle T\rangle$ and aperture $\alpha\in[1,2]$, the Carleson box is
\[
  Q(\alpha I):=\{(\sigma,t): |t-T|\le \alpha L,\ 0<\sigma\le \alpha|I|\},\qquad
  \Omega(I):=\{\tfrac12+\sigma+it: (\sigma,t)\in Q(\alpha I)\}\subset\Omega.
\]

\paragraph{Boundary phase density.} With boundary phase $w(t)$ one has on $I$
\[
  \int_I (-w'(t))\,dt\ \le\ \pi\,\mu\big(Q(I)\big),
\]
where $\mu$ is the Carleson/energy measure induced by the neutralized potential.

\paragraph{Locked certificate to (P+).} Independent inputs:
\[
  c_0(\psi),\quad C_H(\psi),\quad C_P(\kappa),\quad C^{(H^1)}_\psi,\quad C_{\mathrm{box}}.
\]
The fixed-aperture embedding gives
\[
  M_\psi\ \le\ \frac{4}{\pi}\,C^{(H^1)}_\psi\sqrt{C_{\mathrm{box}}}.
\]
Hence the boundary certificate
\[
  \Upsilon\ :=\ \frac{C_H(\psi)\,M_\psi + C_P(\kappa)}{c_0(\psi)}\ <\ \frac{\pi}{2},
\]
which forces $w\in[-\tfrac{\pi}{2},\tfrac{\pi}{2}]$ a.e. on the base (condition (P+)).

\paragraph{Poisson and Cayley.} From (P+) and the Poisson integral, $\Re(2\mathcal J)\ge 0$ on $\Omega(I)$, so $2\mathcal J$ is Herglotz. Therefore the Cayley transform is Schur: $|\Theta|\le1$ on $\Omega(I)$.

\paragraph{Removable singularities at $Z(\xi)$.} If $\rho\in Z(\xi)$, boundedness of $\Theta$ on a punctured disc implies $\Theta$ (and hence $\mathcal J$) extends holomorphically across $\rho$.

\paragraph{Globalization/pinch.} Exhaust $\Omega$ by overlapping boxes and use the maximum-modulus pinch to propagate $|\Theta|\le1$ to the interior and exclude zeros of $\xi$ inside $\Omega$. By the functional equation, all nontrivial zeros lie on $\Re s=\tfrac12$; thus RH.

\paragraph{Independence (no circularity).}
\begin{itemize}
  \item $C_{\mathrm{box}}=K_0+K_\xi+\|U_\Gamma\|_{\mathrm{area}}$ with (i) prime tails $K_0$, (ii) $\xi$-block $K_\xi$ (neutralized far-field + near-field), (iii) Archimedean $\Gamma$-term; each bounded independently.
  \item $M_\psi\le \tfrac{4}{\pi}C_\psi^{(H^1)}\sqrt{C_{\mathrm{box}}}$ via fixed-aperture $H^1$–BMO/Carleson embedding (one-time numeric evaluation).
\end{itemize}

\paragraph{PSC status.} The Prime–Tail Schur–Covering inequality can be presented separately; the main proof chain to (P+) and RH runs solely through the \emph{product} certificate $\Upsilon$.
