\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}

\title{Operator-Theoretic Program for RH via de Branges--Rovnyak Kernels and Fredholm Matching}
\author{A.I. Collaboration}
\date{\today}

% --- Macros ---
\newcommand{\C}{\mathbb{C}}
\newcommand{\Pset}{\mathcal{P}}
\newcommand{\ReS}{\operatorname{Re}}
\newcommand{\spec}{\mathrm{spec}}
\newcommand{\HS}{\mathcal{S}_2}
\newcommand{\Th}{\Theta}
\newcommand{\Si}{\Sigma}
\newcommand{\ThN}{\Theta_N}
\newcommand{\SiN}{\Sigma_N}
\newcommand{\kN}{K_N}
\newcommand{\Hhp}{\mathbb{H}_{1/2}}
\newcommand{\detTwo}{\det\nolimits_{2}}
\newcommand{\xiFun}{\xi}

% --- Theorem Environments ---
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{hypothesis}[theorem]{Hypothesis}

\begin{document}
\maketitle

\begin{abstract}
We organize an operator-theoretic approach to RH on $\ReS s>1/2$ using a Herglotz base $\Si$ and target transfer $\Th=\zeta^2/E_2$. Unconditional facts: $\Si$ is Herglotz, finite Schur models yield PSD kernels, PSD kernels are closed under locally uniform limits, and determinant matching imposes explicit constraints. The sole remaining statement is that $\Th$ is Schur relative to $\Si$ on $\ReS s>1/2$, which would imply RH via a spectral gap and Fredholm identity.
\end{abstract}

\section{Setup}
\begin{definition}
Let $\Hhp=\{ \ReS s>1/2\}$ and define
\[
\Si(s):=\sum_{p} \frac{p^{-2}}{1-p^{-s}},\quad
E_2(s):=\exp\Big(\sum_p p^{-s}+\tfrac12\sum_p p^{-2s}\Big),\quad
\Th(s):=\zeta(s)^2\,E_2(s)^{-1}.
\]
Set
\[K(s,w):=\frac{1-\Th(s)\overline{\Th(w)}}{\Si(s)+\overline{\Si(w)}}.\]
\end{definition}

\begin{lemma}[Herglotz]
$\Re \Si(s)>0$ on $\{\ReS s>0\}$.
\end{lemma}

\section{Finite models and limits}
\begin{definition}
For $P_N$, define $\SiN,\ThN$ by truncation and $\kN$ as above.
\end{definition}

\begin{lemma}[Convergence]
On $\sigma\ge 1/2+\varepsilon$, $\SiN\to\Si$ and $\ThN\to\Th$ locally uniformly; thus $\kN\to K$.
\end{lemma}

\begin{lemma}[PSD closure]
Locally uniform limits of PSD kernels are PSD.
\end{lemma}

\section{Schur realization and spectral gap}
\begin{proposition}
If $K\succeq 0$, then $\Th$ is a contractive multiplier relative to $\Si$, realized by a conservative colligation. Hence strict contractivity off the critical line.
\end{proposition}

\section{Fredholm matching}
\begin{proposition}[Bookkeeping]
Let $A,B,C,D$ be as in the block model and $S:=D+C(I-A)^{-1}B$. On $\{\ReS s>1\}$,
\[
\log \detTwo(I-T)= -\sum_{k\ge2}\frac{\operatorname{tr}(A^k)}{k} + \log(1-S)+ \operatorname{tr}A.
\]
Matching with $\log \xiFun(s)$ yields constraints (M1)--(M3).
\end{proposition}

\section{Core hypothesis and consequence}
\begin{hypothesis}[Core]
$K\succeq 0$ on $\Hhp\times\Hhp$.
\end{hypothesis}

\begin{theorem}[Conditional RH]
Assuming the Core hypothesis, there is an analytic family $T(s)$ with $\detTwo(I-T(s))=\xiFun(s)$ (normalized at $s=2$) and a spectral gap off $\ReS s=1/2$, hence RH.
\end{theorem}

\end{document}
