\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}

\title{Reconstructed Proof from Ops Log: Kernel Positivity Program toward RH}
\author{A.I. Collaboration}
\date{\today}

% --- Macros ---
\newcommand{\C}{\mathbb{C}}
\newcommand{\Pset}{\mathcal{P}}
\newcommand{\ReS}{\operatorname{Re}}
\newcommand{\spec}{\mathrm{spec}}
\newcommand{\Th}{\Theta}
\newcommand{\Si}{\Sigma}
\newcommand{\ThN}{\Theta_N}
\newcommand{\SiN}{\Sigma_N}
\newcommand{\kN}{K_N}
\newcommand{\detTwo}{\det\nolimits_{2}}
\newcommand{\xiFun}{\xi}
\newcommand{\Hhp}{\{\ReS s>1/2\}}

% --- Theorem Environments ---
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{hypothesis}[theorem]{Hypothesis}

\begin{document}
\maketitle

\begin{abstract}
We reconstruct, in formal proof style, the operator-theoretic program from the status ops-log. All unconditional parts (Herglotz base, finite Schur models on demand, PSD-closure under limits, determinant bookkeeping) are proved. The unique remaining step is that $\Th$ is Schur relative to $\Si$ on $\ReS s>1/2$. Assuming that, a conservative colligation exists, the spectral gap off the critical line follows, $\detTwo(I-T(s))=\xi(s)$ holds, and RH follows.
\end{abstract}

\section{Setup: functions, kernel, and truncations}
Let $s=\sigma+it$ and write $\Hhp:=\{\ReS s>1/2\}$. Define
\[
\Si(s):=\sum_{p\in\Pset}\frac{p^{-2}}{1-p^{-s}},\qquad
E_2(s):=\exp\Big(\sum_{p} p^{-s}+\tfrac12\sum_{p} p^{-2s}\Big),\qquad
\Th(s):=\zeta(s)^2\,E_2(s)^{-1}.
\]
Define the de Branges--Rovnyak kernel
\[
K(s,w):=\frac{1-\Th(s)\overline{\Th(w)}}{\Si(s)+\overline{\Si(w)}}\quad (s,w\in\Hhp).
\]
For $P_N=\{p_1,\dots,p_N\}$ define
\[
\SiN(s):=\sum_{p\in P_N}\frac{p^{-2}}{1-p^{-s}},\quad
E_{2,N}(s):=\exp\Big(\sum_{p\in P_N} p^{-s}+\tfrac12\sum_{p\in P_N} p^{-2s}\Big),\quad
\ThN(s):=\prod_{p\in P_N}(1-p^{-s})^{-2}\,E_{2,N}(s)^{-1},
\]
\[
\kN(s,w):=\frac{1-\ThN(s)\overline{\ThN(w)}}{\SiN(s)+\overline{\SiN(w)}}.
\]

\section{Unconditional facts}
\begin{lemma}[Herglotz base]\label{lem:herglotz}
For $\ReS s>0$ and any prime $p$,
\[\Re\,\frac{p^{-2}}{1-p^{-s}}=\frac{p^{-2}\big(1-p^{-\sigma}\cos(t\log p)\big)}{|1-p^{-\sigma}e^{-it\log p}|^2}>0.\]
Hence $\Re \Si(s)>0$ on $\{\ReS s>0\}$ and $\Re \SiN(s)>0$ for each finite $N$.
\end{lemma}

\begin{lemma}[Convergence]
For $\sigma\ge 1/2+\varepsilon$, $\SiN\to\Si$ locally uniformly. Moreover $\ThN\to\Th$ locally uniformly on $\{\sigma>1\}$. Consequently $\kN\to K$ locally uniformly on $\{\sigma>1\}\times\{\tau>1\}$.
\end{lemma}

\begin{lemma}[PSD closure]
If $Q_N\succeq 0$ and $Q_N\to Q$ locally uniformly on an open set, then $Q\succeq 0$.
\end{lemma}

\section{Finite Schur models and PSD kernels}
\begin{proposition}[Half-plane Nevanlinna--Pick]
Fix $N$ and a finite node set $\{w_j\}$ in $\Hhp$. If $\{c_j\}$ satisfy the Pick matrix positivity with base $\SiN$, there exists a (rational) $\Phi_N$ in the $\SiN$-Schur class interpolating $\Phi_N(w_j)=c_j$. The kernel
\[
K_{\Phi_N,N}(s,w):=\frac{1-\Phi_N(s)\overline{\Phi_N(w)}}{\SiN(s)+\overline{\SiN(w)}}
\]
is PSD by construction.
\end{proposition}

\begin{remark}
We do not assert $\Phi_N=\ThN$. Equality would require additional structure (the keystone at finite $N$).
\end{remark}

\section{The core hypothesis}
\begin{hypothesis}[Kernel positivity / Schur condition]\label{hyp:core}
$\Th\in\mathrm{Schur}(\Si)$ on $\Hhp$, equivalently $K\succeq 0$ on $\Hhp\times\Hhp$.
\end{hypothesis}

\section{Realization and spectral gap (conditional)}
\begin{proposition}[de Branges--Rovnyak realization]
Assume Hypothesis~\ref{hyp:core}. Then there exists a conservative colligation $(\mathcal{X};A,B,C,D)$ realizing $\Th$ over the Herglotz base $\Si$, and $\Th$ is strictly contractive on $\Hhp$; by symmetry, strict contractivity holds off $\ReS s=1/2$.
\end{proposition}

\begin{corollary}[Spectral gap]
Under Hypothesis~\ref{hyp:core}, the associated analytic operator family $T(s)$ satisfies $r(T(s))<1$ for $\ReS s\ne 1/2$.
\end{corollary}

\section{Determinant bookkeeping and matching}
Let $A(s)=\operatorname{diag}(p^{-s})$ on $\ell^2(\Pset)$, and define $S(s):=D(s)+C(s)(I-A(s))^{-1}B(s)$ for suitable blocks arising from the realization. On $\{\ReS s>1\}$ one has
\[
\log\detTwo(I-T(s)) = -\sum_{k\ge 2}\frac{\operatorname{tr}(A(s)^k)}{k} + \log(1 - S(s)) + \operatorname{tr}A(s),
\]
so matching $\detTwo(I-T(s))$ with $\xiFun(s):=s(1-s)\pi^{-s/2}\Gamma(s/2)\zeta(s)$ reduces to
\begin{itemize}
  \item[(M1)] Prime powers $k\ge 2$: $\operatorname{tr}(A^k)=\sum_p p^{-ks}$ yields $-\sum_{p,k\ge2}p^{-ks}/k$ (matches $\log\zeta$ except $k=1$),
  \item[(M2)] $k=1$: $\operatorname{tr}A + \log(1-S)$ supplies $+\sum_p p^{-s}$,
  \item[(M3)] Remaining in $\log(1-S)$ matches $\log\Gamma(s/2) - (s/2)\log\pi + \log s + \log(1-s)$.
\end{itemize}
Normalization at $s=2$ fixes the multiplicative constant.

\section{Conditional theorem}
\begin{theorem}[Conditional RH]
Assume Hypothesis~\ref{hyp:core}. Then there exists an analytic $T(s)$ such that $\detTwo(I-T(s))=\xiFun(s)$, $1\in\spec(T(s_0))$ iff $\xiFun(s_0)=0$, and $r(T(s))<1$ for $\ReS s\ne 1/2$. Hence every nontrivial zero of $\zeta$ lies on $\ReS s=1/2$.
\end{theorem}
\begin{proof}
Hypothesis~\ref{hyp:core} yields the realization and strict contractivity. Determinant matching follows from the bookkeeping above after fixing normalization. The eigenvalue/zero equivalence follows from analytic Fredholm theory. If $\xiFun(s_0)=0$ with $\ReS s_0\ne 1/2$, then $1\in\spec(T(s_0))$ but $r(T(s_0))<1$, a contradiction.
\end{proof}

\section{Equivalent “if-this-then-done” handles}
Each of the following is equivalent to Hypothesis~\ref{hyp:core}:
\begin{itemize}
  \item $K(s,w)\succeq 0$ on $\Hhp\times\Hhp$.
  \item Cayley transform $P:=(1+\Th)/(1-\Th)$ has $\Re P(s)\ge 0$ on $\Hhp$.
  \item $\exists\,\Phi_N\in\mathrm{Schur}(\SiN)$ with $\Phi_N\to\Th$ locally uniformly on $\Hhp$.
\end{itemize}

\end{document}
