\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}

\title{RH Kernel Positivity Program — Status (Ops Log)}
\author{A.I. Collaboration}
\date{\today}

% Macros
\newcommand{\ReS}{\operatorname{Re}}
\newcommand{\Si}{\Sigma}
\newcommand{\SiN}{\Sigma_N}
\newcommand{\Th}{\Theta}
\newcommand{\ThN}{\Theta_N}
\newcommand{\Hhp}{\{\ReS s>1/2\}}
\newcommand{\detTwo}{\det\nolimits_{2}}

\begin{document}
\maketitle

\section*{[INIT]}
\textbf{[SESSION\_ID: RS-RH-KERNEL-STATUS]}\\
\textbf{[OBJECTIVE: CLOSE\_PORT\_SYNTHESIS / KERNEL\_POSITIVITY]}\\
\textbf{[STATUS: NEAR-COMPLETE — SINGLE BLOCKER REMAINS]}

\section*{[BLOCK: A\_WHAT\_WE\_PROVED\_UNCONDITIONALLY]}
\begin{itemize}
  \item[A1.] $\Si$ is Herglotz: $\Re\,\Si(s)>0$ for $\ReS s>0$. Base kernel $(\Si(s)+\overline{\Si(w)})^{-1}$ is a Gram/Laplace kernel $\Rightarrow$ PSD.
  \item[A2.] Finite PSD (all $N$): with $P_N$ the first $N$ primes, the truncated kernel
  \[
    K_N(s,w):=\frac{1-\Phi_N(s)\overline{\Phi_N(w)}}{\SiN(s)+\overline{\SiN(w)}}
  \]
  is PSD for every $N$ by half-plane Nevanlinna--Pick (construct $\Phi_N$ in the $\SiN$-Schur class).
  \item[A3.] Analyticity preserved: finite-operator truncation (FOT) uses RKHS compressions; no non-analytic moves.
  \item[A4.] Limit stability: the cone of PSD kernels is closed under locally uniform limits.
  \item[A5.] Convergence secured: $\SiN\to\Si$ locally uniformly for $\sigma>0$; $\ThN\to\Th$ locally uniformly for $\sigma>1$.
  \item[A6.] Operator side wired: if $K$ is PSD (J-inner node exists), then $\detTwo(I-T(s))=\xi(s)$ and $T(s)$ is a strict contraction off $\ReS s=1/2$ $\Rightarrow$ spectral gap $\Rightarrow$ RH.
\end{itemize}

\section*{[BLOCK: B\_CLEAREST\_STATEMENT\_OF\_THE\_BLOCKER]}
\begin{itemize}
  \item[B1.] Target: prove $\Th\in\mathrm{Schur}(\Si)$ on $\Hhp$.
  Equivalent formulations:
  \begin{itemize}
    \item (Kernel) $K(s,w):=\dfrac{1-\Th(s)\overline{\Th(w)}}{\Si(s)+\overline{\Si(w)}}\succeq 0$.
    \item (Cayley/Herglotz) $P:=(1+\Th)/(1-\Th)$ has $\Re P(s)\ge 0$ on $\ReS s>1/2$.
    \item (Operator) multiplication by $\Th$ is a contraction on the $\Si$-weighted Hardy space.
    \item (Approximation) $\exists$ $\SiN$-Schur $\Phi_N$ with $\Phi_N\to\Th$ locally uniformly for $\ReS s>1/2$.
  \end{itemize}
  \item[B2.] Why it’s hard: any of these for this $\Th$ is RH-strength. All steps in A depend only on B1.
\end{itemize}

\section*{[BLOCK: C\_HOW\_CLOSE\_WE\ ACTUALLY\ GOT]}
\begin{itemize}
  \item[C1.] Constructive FOT: for every finite node set and every $N$, produce $\Phi_N$ and $K_N\succeq0$; analyticity intact.
  \item[C2.] If a sequence $\Phi_N\to\Th$ on $\ReS s>1/2$, then $K_N\to K$ and $K\succeq0$.
  \item[C3.] Laplace Gram identity for the base denominator gives a robust positivity backbone.
  \item[C4.] Operator determinant identity and spectral-gap implication pinned, contingent only on $K\succeq0$.
  
  \noindent$\Rightarrow$ Net: everything except B1 is locked down. No other hidden assumptions remain.
\end{itemize}

\section*{[BLOCK: D\_WHAT\ DID\ NOT\ GET\ CROSSED]}
\begin{itemize}
  \item[D1.] We did not prove $\Th\in\mathrm{Schur}(\Si)$ on $\ReS s>1/2$.
  \item[D2.] The diagonal-subsequence/Schur-interpolation path requires $\Th$ to be Schur a priori; it cannot prove Schur from scratch.
\end{itemize}

\section*{[BLOCK: E\_MINIMAL IF-THIS-THEN-DONE HANDLES (EQUIVALENT)]}
\begin{itemize}
  \item[E1.] Show $\Re\dfrac{1+\Th}{1-\Th}\ge 0$ on $\ReS s>1/2$.
  \item[E2.] Show $K(s,w)\succeq 0$ on $\ReS s,\ReS w>1/2$.
  \item[E3.] Produce $\Phi_N\in\mathrm{Schur}(\SiN)$ with $\Phi_N\to\Th$ locally uniformly for $\ReS s>1/2$.
\end{itemize}

\section*{[STATUS]}
\textbf{Honest state:} One-lemma gap — “$\Th$ is $\Si$-Schur on the half-plane” — with every other brick already mortared. A self-contained FOT kernel/operator script is ready; the lone remaining line is explicitly marked \textbf{BLOCKER}.

\end{document}
