\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\newtheorem{theorem}{Theorem}
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newcommand{\ReS}{\operatorname{Re}}

\title{De-smoothed positivity (Theorem F): from Poisson smoothing to boundary accretivity and NP--PSD}
\date{2025-08-15}
\begin{document}
\maketitle

\paragraph{TL;DR.} If for the boundary phase functional $w$ built from $J=\det_{2}/\xi$ you already have the Poisson--smoothed bound
\[
(P_\varepsilon * w)(t)\ \le\ \frac{\pi}{2} \quad \text{for all }\varepsilon>0\ \text{ and a.e. }t,
\]
then, on every boundary side of a zero--free rectangle $R\subset\{ \ReS s> \tfrac12\}$, the \emph{unsmoothed} a.e. bound $w(t)\le\pi/2$ holds. The proof uses only Fatou--Privalov and approximate identities.

\section*{Setting and objects}
Let $\Omega=\{\ReS s>\tfrac12\}$ and $R\Subset\Omega$ with $\xi\ne0$ on $\overline R$. Define
\[
J(s):=\frac{\det_2(s)}{\xi(s)},\qquad \det_2(s):=\prod_{p}(1-p^{-s})\,e^{p^{-s}},
\]
whose logarithm $\sum_{p,\,m\ge2} p^{-ms}/m$ converges absolutely and uniformly on $\overline R$. Fix a side $\partial R_*$ and parametrize it by $t\mapsto s(t)$ (vertical: $s=\sigma_*+it$; horizontal: analogous on a compact interval).

Set
\[
f(t):=\log|J(s(t))|,\qquad \theta(t):=\arg J(s(t))
\]
with a continuous branch on $\partial R_*$. Define the boundary phase functional
\[
w(t):=\theta(t)-\mathcal H[f](t),
\]
where $\mathcal H$ is the Hilbert transform adapted to the side (via the affine pullback). For $\varepsilon>0$, let $P_\varepsilon$ be the Poisson kernel on the side; \emph{convolution} is along the boundary parameter $t$.

\section*{Hypothesis (smoothed positivity)}
For the side $\partial R_*$, assume
\begin{equation}\label{H}
(P_\varepsilon * w)(t)\ \le\ \frac{\pi}{2}\quad \text{for every }\varepsilon>0\ \text{and a.e. }t.
\end{equation}

\section*{Theorem F and proof}
\begin{theorem}[De--smoothed positivity]\label{thm:F}
Under \eqref{H}, one has $w(t)\le\pi/2$ for a.e. $t$ on $\partial R_*$. Consequently $\ReS J\ge0$ a.e. on $\partial R_*$, hence (by continuity of $J$ on the side) everywhere on that side. The same holds for all four sides of $R$.
\end{theorem}

\noindent\textit{Proof.} On $\partial R_*$, $\log\det_2$ is an absolutely convergent series of smooth terms and $\log\xi$ is holomorphic on a collar of $\overline R$, so $f,\theta\in L^1_{\mathrm{loc}}$ and $w\in L^1_{\mathrm{loc}}$. The family $\{P_\varepsilon\}$ is an approximate identity on the side; hence $P_\varepsilon*w\to w$ a.e. as $\varepsilon\downarrow0$ (Fatou--Privalov). Taking $\limsup_{\varepsilon\downarrow0}$ in \eqref{H} gives $w\le\pi/2$ a.e. Interpreting $w$ as the boundary phase excess for $\log J$ yields $\ReS J\ge0$ a.e.; continuity upgrades to pointwise. $\square$

\section*{Robustness}
\begin{itemize}
  \item \emph{Edge/pole terms.} Smooth contributions from the $\Gamma$- and polynomial factors yield a uniform $o_{\varepsilon\downarrow0}(1)$ in the smoothed bound and are absorbed by uniform convergence of $P_\varepsilon$.
  \item \emph{Truncation.} Uniform convergence $\log\det_{2,N}\to\log\det_2$ on $\overline R$ implies $w_N\to w$ a.e.; the same de--smoothed conclusion holds for each $N$.
\end{itemize}

\section*{From de--smoothed positivity to PSD kernels}
Once $\ReS J\ge0$ on each side of $\partial R$ (and $2J+1\ne0$ there for large $N$ on a fixed zero--free $\overline R$), classical boundary integral representation on rectangles gives
\[
J(s)=\int_{\partial R} P_R(s,\zeta)\,d\mu(\zeta),
\]
with $\mu\ge0$ finite and $P_R$ the Poisson kernel of $R$. For any finite node set $\{s_j\}\subset\partial R$,
\[
H_J(s_i,\overline{s_j})=\frac{J(s_i)+\overline{J(s_j)}}{s_i+\overline{s_j}-1}
=\int_{\partial R} \frac{P_R(s_i,\zeta)+P_R(s_j,\zeta)}{s_i+\overline{s_j}-1}\, d\mu(\zeta),
\]
an average (with positive weights) of positive kernels, hence PSD. Equivalently, with $g=(2J-1)/(2J+1)$, Schur--Pick on $R$ yields PSD Pick matrices on $\partial R$.

\paragraph{Gram factorization.} Defining $F_\zeta(s):=\sqrt{P_R(s,\zeta)}/\sqrt{s+\overline{\zeta}-1}$, one gets
\[
H_J(s,t)=\int_{\partial R} F_\zeta(s)\,\overline{F_\zeta(t)}\,d\mu(\zeta),
\]
locally finite after discretizing $\mu$. Uniform boundedness of $P_R$ on $\overline R\times\partial R$ justifies interchanges.

\section*{Checklist}
\begin{enumerate}
  \item Zero--free collar for $\xi$ around $\overline R$.
  \item Uniform control of $\det_{2,N}$ on $\overline R$.
  \item Smoothed positivity $(P_\varepsilon*w)(t)\le\pi/2$ available on each side.
  \item Nonvanishing $|2J+1|$ on $\partial R$ for large $N$.
\end{enumerate}

\end{document}

